### 2017-06-01 paper/lexicographic.tex
started writing the proof of LexRSM soundness

\begin{definition}[Lexicographic Ranking Supermartingale]
Let $(\Omega,\genfilt,\probm)$ be a probability space, 
$\{\genfilt_i\}_{i=0}^{\infty}$ a filtration of $\genfilt$, $\stime$ a stopping 
time w.r.t. that filtration, and 
$\eps\geq 0$. 
An $n$-dimensional stochastic process $\{\vec{X}_{i}\}_{i=0}^{\infty}$ is a 
\emph{lexicographic $\eps$-ranking supermartingale for $\stime$ 
($\eps$-LexRSM)} if the 
following 
conditions hold:
\begin{compactenum}
\item For each $1\leq j \leq n$ the 1-dimensional stochastic process 
$\{\vecseq{X}{i}{j}\}_{i=0}^{\infty}$ is adapted to 
$\{\genfilt_i\}_{i=0}^{\infty}$.
\item For each $i\in \Nset_0$ and each $1\leq j \leq n$ it holds 
$\E[|\vecseq{X}{i}{j}|]<\infty$.
\item For each $i\in \Nset_0$ there exists $1\leq j \leq n$ such that
\begin{compactitem}
	\item $\E[\vecseq{X}{i+1}{j}\mid \genfilt_i]\leq\vecseq{X}{i}{j} - 
	\eps\cdot \vec{1}_{\stime > i} $; and
	\item for all $1 \leq j' < j$ it holds $\E[\vecseq{X}{i+1}{j'}\mid 
	\genfilt_i]\leq\vecseq{X}{i}{j'}$.
\end{compactitem}
\end{compactenum}
\end{definition}

>>>>

\begin{definition}[Lexicographic Ranking Supermartingale]
Let $(\Omega,\genfilt,\probm)$ be a probability space, 
$\{\genfilt_i\}_{i=0}^{\infty}$ a filtration of $\genfilt$, $\stime$ a stopping 
time w.r.t. that filtration, and 
$\eps\geq 0$. 
An $n$-dimensional stochastic process $\{\vec{X}_{i}\}_{i=0}^{\infty}$ is a 
\emph{lexicographic $\eps$-ranking supermartingale for $\stime$ 
($\eps$-LexRSM)} if the 
following 
conditions hold:
\begin{compactenum}
\item For each $1\leq j \leq n$ the 1-dimensional stochastic process 
$\{\vecseq{X}{i}{j}\}_{i=0}^{\infty}$ is adapted to 
$\{\genfilt_i\}_{i=0}^{\infty}$.
\item For each $i\in \Nset_0$ and each $1\leq j \leq n$ it holds 
$\E[|\vecseq{X}{i}{j}|]<\infty$.
\item For each $i\in \Nset_0$ and each $\omega\in \Omega$ with 
$\stime(\omega)>i$ there exists $1\leq j 
\leq n$ such that
\begin{compactitem}
	\item $\E[\vecseq{X}{i+1}{j}\mid 
	\genfilt_i](\omega)\leq\vecseq{X}{i}{j}(\omega) - 
	\eps$; and
	\item for all $1 \leq j' < j$ it holds $\E[\vecseq{X}{i+1}{j'}\mid 
	\genfilt_i](\omega)\leq\vecseq{X}{i}{j'}(\omega)$.
\end{compactitem}
\item For each $\omega \in \Omega$ and $i\in \Nset_0$ it holds 
$\stime(\omega)>i 
\Rightarrow \vec{X}_i (\omega)\geq \vec{0}$ (componentwise).
\end{compactenum}
\end{definition}

\begin{theorem}
Let $(\Omega,\genfilt,\probm)$ be a probability space, 
$\{\genfilt_i\}_{i=0}^{\infty}$ a filtration of $\genfilt$, and $\stime$ a 
stopping 
time w.r.t. that filtration. If there exists an $\eps$-LexRSM for $\stime$, 
then $\probm(\stime<\infty)=1$.
\end{theorem}
\begin{proof}
The proofs proceeds by contradiction, i.e. we assume that an $\eps$-LexRSM for 
$\stime$ exists and $\probm(\stime=\infty)>0$. For succinctness we denote the 
set $\{\omega\mid \stime(\omega)=\infty\}$ by $\genRunSet_{\infty}$.

For $\omega\in \Omega$ we define the level of $\omega$ at step $i$ to be the 
number $\levelrank{\omega}{i}$ equal to either $0$, if $\stime(\omega)\leq i$, 
or otherwise to the smallest $1\leq j \leq n$ such that 
$\E[\vecseq{X}{i+1}{j}\mid 
\genfilt_i](\omega)\leq\vecseq{X}{i}{j}(\omega)-\eps$. By the definition of 
$\eps$-LexRSM the value $\levelrank{\omega}{i}$ is well-defined for all 
$\omega$. 
%\[
%\levelrank{\omega}{i} = \begin{dcases}
%0 & \text{if $\stime(\omega)\leq i$} \\
% 
%\end{dcases}
%\]
\end{proof}
